
% - - - My Curriculum Vitae - - - 

% Thanks to Thomas Jansson for template/class
% http://www.tjansson.dk/?p=604
% which originally came from here:
% http://linux.dsplabs.com.au/?p=54
% which itself was inspired by:
% http://www.biostat.harvard.edu/~paciorek/computingTips/computingTips.html

\documentclass[margin,line,a4paper]{resume}

\usepackage[usenames,dvipsnames]{color}
\usepackage[colorlinks]{hyperref}
% after this we set web links to blue and mail links to blue

\begin{document}
\name{\LARGE Will Gallia}

\begin{resume}

% - - - Contact - - - 
\section{\mysidestyle Contact}

\hypersetup{urlcolor=Fuchsia}
\href{mailto:wgallia@gmail.com}{wgallia@gmail.com} \hfill
\hypersetup{urlcolor=RoyalBlue}
\href{http://wgallia.com}{http://wgallia.com} \hfill
+447944137483 \\

% - - - Profile - - - 
% \section{\mysidestyle Interests}
% I am interested in the creative potential of programming and where art meets computation.

% - - - Experience - - - 
\section{\mysidestyle Employment}

\textbf{Goldsmiths College}, London \vspace{1mm}\\
\textsl{Research Assistant} \hfill 01.2014 - 11.2014 \vspace{2mm} \\
I was awarded a full PhD studentship in Computational Art \& Technology. The first six months were spent
working in a partnership with five London based startups through
\href{http://www.theworkfoundation.com/Aboutus/London-Creative-and-Digital-Fusion}{London
  Fusion}, where I worked on a variety of tools and applications, mostly using Python. Later the
focus of the work moved on to machine learning audio and images in
order to generate media.


\textbf{Polkima}, Izmir \vspace{1mm}\\
\textsl{Computer Programmer} \hfill 10.2013 - 01.2014 \vspace{2mm} \\
I resolved various computing problems for Polkima, a glass reinforced plastics producer in Turkey. This involved programming a Comau industrial robot in the PDL2
domain specific language to trim tractor engine bonnets. I also wrote multiple tools in Excel VBA to automate invoice generation, product
verification and other accounting tasks.


\textbf{Matt Watkins Design}, London \vspace{1mm}\\
\textsl{iOS Programmer} \hfill 05.2012 - 10.2012 \vspace{2mm} \\
I was the sole developer for
\href{http://wurfelmosaik.com/}{W\"{u}rfel-Mosaik}, a digital version
of the classic Swiss children`s game of the same name. The iPhone/iPad
application makes considerable use of iCloud, Core Graphics and social
networking APIs.

\textbf{Hellicar \& Lewis}, London \vspace{1mm}\\
\textsl{Interaction Designer} \hfill 06.2012 - 08.2012 \vspace{2mm} \\
I worked in a team of three developers creating
\href{http://www.hellicarandlewis.com/intel/}{Triptych},
a set of interactive installations showcasing Intel's new range of
processors. Interaction was through a Microsoft Kinect sensor and
large projections. The projects were programmed in C++ \& GLSL and
used openFrameworks. The project was
\href{https://github.com/HellicarAndLewis/Triptych}{open source}.

\textbf{greyworld}, London  \vspace{1mm}\\
\textsl{Computer Programmer} \hfill 07.2010 - 09.2010 \vspace{2mm} \\
I worked on real-time generative visuals for London
based art collective \href{http://greyworld.org}{greyworld} and
advertising agency Ogilvy. The project was built with Processing.


% - - - Education - - -
\section{\mysidestyle Education}

\textbf{Imperial College}, London \vspace{0.5mm}\\
\textsl{MSc Computing - Visual Information Processing} (Merit) \hfill 10.2012 - 09.2013 \vspace{1mm}
% Dissertation: \emph{Neighbourbood Approximation Forest based Segmentation}

\textbf{Goldsmiths College}, London \vspace{0.5mm}\\
\textsl{BSc Creative Computing} (First w/ Undergraduate Prize) \hfill 09.2009 - 05.2012 \vspace{1mm}
% Dissertation: \emph{Construct: Voxel based visual hulls}

\textbf{Clifton College}, Bristol \vspace{0.5mm}\\
\textsl{Peter Brook (All Round) Scholarship} \hfill 09.2002 - 06.2007 \vspace{0.5mm} \\
A-Level: Maths: A, Physics: A, Chemistry: B


% - - - Teaching Experience - - -
\section{\mysidestyle Teaching Experience}

\textbf{Goldsmiths College}, London \vspace{1mm}\\
\textsl{Teaching Assistant} \hfill 01.2013 - 11.2014 \vspace{2mm} \\
I have assisted at all undergraduate level courses, such as Introduction to \ Programming using Processing, Maths and Perception \& Multimedia Computing. I have also helped in  MA programming labs, teaching C++ with openFrameworks.

% \textbf{Swanlea School}, Whitechapel, London \vspace{1mm}\\
% \textsl{Assistant Teacher} \hfill 03.2011 - 04.2011 \vspace{2mm} \\
% As part of the TDA’s Student Associate scheme, I worked alongside
% teachers in both the Science and Maths departments, teaching students at GCSE level.

% \newpage
% - - - Skills  - - - 
\section{\mysidestyle Skills}

\textbf{Audio Visual Computer Programming} \vspace{1mm} \\
I have programming experience in a number of environments and I am
familiar with a wide range of tools. For realtime projects I primarily work in
\textbf{C++}, using OpenGL (\textbf{GLSL}) and possibly utilising
libraries such as \textbf{openFrameworks} or \textbf{Cinder}. For mobile applications I like to use iOS with \textbf{Objective-C}.  I have considerable experience working with audio at the buffer.

\textbf{Web based Programming} \vspace{1mm} \\
I have worked in the back and front end of the web domain. I recently won the Spotify prize for a \textbf{Javascript} based music mixing application at the London Music Hackday. I have also built database driven serverside applications with \textbf{Python} using django and also with \textbf{PHP}. I have experience with a range of databases, from \textbf{MySQL}/\textbf{Postgres} to \textbf{MongoDB}.

\textbf{Machine Learning} \vspace{1mm} \\
I have experience in implementing machine learning and signal processing algorithms in \textbf{GNU Octave}/\textbf{MATLAB} and \textbf{Python}. At a postgraduate level, I have researched various modern techniques for learning and prediction.

\textbf{Embedded Programming and Electronics} \vspace{1mm} \\
I have an interest in embedded programming where I usually write firmware in \textbf{C}. I
frequently use the \textbf{Arduino} to prototype, though I have also built projects from the ground up.

\section{\mysidestyle Interests}

\textbf{Cycling}: London $\rightarrow$ Munich (solo), route: \href{http://where.is.wgallia.com}{http://where.is.wgallia.com} \vspace{1mm} \\
\textbf{German}: European Common Framework Level A2

% \section{\mysidestyle Languages}
% English \& Turkish

%- - - References - - -
% \section{\mysidestyle{References}}

% %set colours for email...
% \hypersetup{urlcolor=Fuchsia}
% %
% \textbf{Dr. Daniel Rueckert}, Tutor: \href{mailto:d.rueckert@imperial.ac.uk}{d.rueckert@imperial.ac.uk}
% \vspace{2mm} \\
% \textbf{Dr. Mick Grierson}, Tutor: \href{mailto:m.grierson@gold.ac.uk}{m.grierson@gold.ac.uk}
% \vspace{2mm} \\
% \textbf{Matt Watkins}: \href{info@wurfelmosaik.com}{info@wurfelmosaik.com}
% \vspace{2mm} \\

\end{resume}
\end{document}
